A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2016-10-03 doc/paper1-submission/paper4.tex
Make abstract a bit more explicit.

\documentclass[fleqn,12pt,english]{wlpeerj}
\usepackage[T1]{fontenc}
%\usepackage[latin9]{inputenc}
%\usepackage{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
%\usepackage{xcolor}
%\usepackage{verbatim}
\usepackage{float}
\usepackage{fancybox}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{natbib}

@@

\author[1,2]{Benjamin D. Redelings}
\author[2,3,4]{Mark T. Holder}
\affil[1]{Department of Biology, Duke University, Durham NC, US}
\affil[2]{Department of Ecology and Evolutionary Biology, University of Kansas, Lawrence KS, US}
\affil[3]{Biodiversity Institute, University of Kansas, Lawrence KS, US}
\affil[4]{Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, 69118 Heidelberg, Germany}
\corrauthor[2,3,4]{Mark T. Holder}{mtholder@ku.edu}

@@

\begin{abstract}
We present a new supertree method and software implementation that
enables rapid estimation of a summary tree on the scale of millions
of leaves. This software pipeline is called \emph{``propinquity.''}
It uses the dependency-tracking tool \emph{make} to direct the series
of operations required to construct the tree. It relies heavily on
\emph{``otcetera''} - a set of C++ tools to performs most of the
steps of the pipeline. All of the components are free software and
are available on GitHub. This pipeline is currently used by the Open
Tree of Life project to produce all of the versions of project's ``synthetic
tree'' starting at version 5. The propinquity-based pipeline improves
on previous supertree construction methods because it produces no
unsupported branches, and it avoids unnecessary polytomies. In addition
to producing a tree, the pipeline writes an annotations file that
reports which grouping in the input trees support each of the groups
in the supertree.
\end{abstract}

>>>>

\documentclass[fleqn,12pt,lineno,english]{wlpeerj}
\usepackage[T1]{fontenc}
%\usepackage[latin9]{inputenc}
%\usepackage{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
%\usepackage{xcolor}
%\usepackage{verbatim}
\usepackage{float}
\usepackage{fancybox}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{natbib}

@@

\author[1,2]{Benjamin D. Redelings}
\author[2,3,4]{Mark T. Holder}
\affil[1]{Department of Biology, Duke University, Durham NC, US}
\affil[2]{Department of Ecology and Evolutionary Biology, University of Kansas, Lawrence KS, US}
\affil[3]{Biodiversity Institute, University of Kansas, Lawrence KS, US}
\affil[4]{Heidelberg Institute for Theoretical Studies, Heidelberg, Germany}
\corrauthor[2,3,4]{Mark T. Holder}{mtholder@ku.edu}

@@

\begin{abstract}
We present a new supertree method that enables rapid estimation of a
summary tree on the scale of millions of leaves.  This supertree
summarizes a collection of input phylogenies and an input taxonomy.
We introduce formal requirements that such a supertree must satisfy in
order to transparently and justifiably represent the input trees.   In
addition to producing a tree, our method writes an annotations file
that reports which grouping in the input trees support each of the
groups in the supertree.

We compare the performance of this new method to a previous supertree
method on the inputs to the Open Tree of Life version 4, and find that
the number of displayed input splits increases from 35,518 to 39,639 and the
number of conflicting input splits decreases from 2760 to 1357.  The
new supertree method also improves on the previous supertree
construction method because it produces no unsupported branches, and
it avoids unnecessary polytomies.

This pipeline is currently used by the Open Tree of Life project to
produce all of the versions of project's ``synthetic tree'' starting
at version 5.This software pipeline is called
\emph{``propinquity.''}. It relies heavily on \emph{``otcetera''} - a
set of C++ tools to perform most of the steps of the pipeline. All of
the components are free software and are available on GitHub.
\end{abstract}
